---
title: "p8105_hw3_wc2788"
author: "Wen Cheng"
date: "10/17/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Problem 1

load the data from  p8105.datasets
```{r} 
library(p8105.datasets)
data("instacart")
```
This dataset contains `r nrow(instacart)` rows and `r ncol(instacart)` columns, where each row in the dataset is a product from an order.

How many aisles are there, and which aisles are the most items ordered from?
```{r}
instacart %>% 
  count(aisle) %>% #count how many aisles
  arrange(desc(n)) #find the most items ordered
```
There are 134 aisles, and fresh vegetables are most ordered. 

Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.
```{r}
instacart %>% 
  count(aisle) %>% 
  filter(n > 10000) %>% #only show more than 10000
  mutate(aisle = factor(aisle), 
         aisle = fct_reorder(aisle, n)) %>% 
  ggplot(aes(x = aisle, y = n)) + 
  geom_point() + 
  theme(axis.text.x = element_text(angle = 90)) + #easy to read
  labs(title = "aisles with more than 10,000 items ordered",
       x = "aisle",
       y = "number of items ordered") #clear named
```

Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.
```{r}
instacart %>%
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% #select aisles
  group_by(aisle) %>%
  count(product_name) %>%
  mutate(rank = min_rank(desc(n))) %>% #make a rank variable
  filter(rank <= 3) %>% #most popular three
  arrange(aisle, rank) %>%
  knitr::kable() #make a table
```


## Problem 2

```{r}

```

## Problem 3

```{r}

```
